Additional analysis

### 2018-06-25 03_additional-analysis.Rmd
Plot average time

# Load libraries again
library(tidyverse)
library(magrittr)
library(rstanarm)
library(broom)
library(coda)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
results %>% 
  summarize_at(vars(duration), funs(min, max, mean, sd, median)) %>% 
  gather(Statistic, value) %>% 
  mutate(value = seconds_to_period(value)) %>% 
  mutate(Minutes = sprintf("%02.0f:%02.0f", minute(value), second(value))) %>% 
  select(-value) %>% 
  pandoc.table()
```

## Attention check #2

```{r attention-check-2, results="asis"}
results %>% count(attention2_correct) %>% 
  rename(`Attention check 2 correct` = attention2_correct, Count = n) %>% 
  pandoc.table()
```

>>>>

# Load libraries again
library(tidyverse)
library(magrittr)
library(rstanarm)
library(broom)
library(coda)
library(glue)
library(ggstance)
library(ggridges)
library(grid)
library(gridExtra)
library(Gmisc)
library(patchwork)
library(pander)
library(scales)
library(huxtable)
library(lubridate)
library(modelr)
library(here)

@@

```{r avg-time, results="asis"}
fmt_ms <- function(x) {
  n_seconds <- seconds_to_period(x)
  sprintf("%02.0f:%02.0f", minute(n_seconds), second(n_seconds))
}

theme_ngos_table <- ttheme_minimal(
  core = 
    list(fg_params = 
           list(hjust = 0, x = 0.1,
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed Light"),
         bg_params = list(fill = "white")),
  colhead = 
    list(fg_params = 
           list(hjust = 0, x = 0.1, col = "white",
                fontsize = 7, fontface = "plain",
                fontfamily = "Encode Sans Condensed SemiBold"),
         bg_params = list(fill = ngo_cols("blue"))),
  padding = unit(c(4, 2), "mm"))

time_summary <- results %>% 
  summarize_at(vars(duration), funs(Minimum = min, Maximum = max, Mean = mean, 
                                    `Standard deviation` = sd, Median = median)) %>% 
  gather(Statistic, value) %>% 
  mutate(Minutes = fmt_ms(value)) %>% 
  select(-value)

pandoc.table(time_summary)
```

```{r avg-time-plot, fig.height=2.5, fig.width=4}
summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
  gtable::gtable_add_grob(., grobs = rectGrob(gp = gpar(fill = NA, lwd = 1)),
                          t = 1, b = nrow(.), l = 1, r = ncol(.))

plot_avg_time <- ggplot(results, aes(x = duration)) +
  geom_histogram(bins = 50, fill = ngo_cols("blue")) +
  scale_x_time(labels = fmt_ms) +
  annotation_custom(summary_stats, xmin = 700, xmax = 900, ymin = 30, ymax = 60) +
  labs(x = "Minutes spent on experiment", y = "Count") +
  theme_ngos() +
  theme(panel.grid.minor = element_blank())

plot_avg_time %T>% 
  print() %T>%
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.pdf"),
         width = 4, height = 2.5, units = "in", device = cairo_pdf) %>% 
  ggsave(., filename = file.path(here(), "output", "figures", "avg-time.png"),
         width = 4, height = 2.5, units = "in", type = "cairo", dpi = 300)
```
